A Generalized Sphere Theorem for Positively Curved Combinatorial 3-Manifolds

### 2013-04-14 paper/paper.tex
more writing

\section{Results}
We are now finally able to state our main result, which shows that any positively curved 3-manifold with diameter larger than half that allowed by Corollary \ref{thm:discrete_BM_expanded_paths}.

\begin{thm} Any positively curved combinatorial 3-manifold $M$ with $diam(M)>J$ is homeomorphic to the 3-sphere.
\label{thm:discrete_GS}
\end{thm}

diameter statistics by topological type

\begin{tabular} {| l l | l l | l l | l l | l l |}
\hline
\multicolumn{2}{|c|}{$S^{3}/Q$} &
\multicolumn{2}{|c|}{$L(3,1)$} &
\multicolumn{2}{|c|}{$RP^{3}$} &
\multicolumn{2}{|c|}{$S^{3}$} &
\multicolumn{2}{|c|}{$L(4,1)$} \\
\hline
\hline
$1H$&1    &$2E$&1    &$1H$&10    &$1E$&3    &$1J$&1 \\
  &       &$1J$&1    &$2E$&7     &$1H$&173  &    &  \\
  &       &  &       &$1J$&5     &$2E$&401  &    &  \\
  &       &  &       &    &      &$1J$&2438 &    &  \\
  &       &  &       &    &      &$3E$&1060 &    &  \\
  &       &  &       &    &      &$2H$&582  &    &  \\
  &       &  &       &    &      &$4E$&93   &    &  \\
  &       &  &       &    &      &$2J$&11   &    &  \\
\hline
\end{tabular}

global diameter statistics by topological type

@@

>>>>

\section{Main Results}

We are now finally able to state our main result, which shows that any positively curved 3-manifold with diameter larger than half that allowed by Corollary \ref{thm:discrete_BM_expanded_paths}.

\begin{thm} Any positively curved combinatorial 3-manifold $M$ with $diam(M)>J$ is homeomorphic to the 3-sphere. This bound is sharp, and equal to half the maximum diameter which occurs for any such $M$.
\label{thm:discrete_GS}
\end{thm}

\noindent The proof of this result relies on a complete census of positively curved combinatorial 3-manifolds completed by Lutz and Sullivan. The census contains 4787 manifolds and contains examples of the 3-sphere $S^3$, the real projective space $\mathbb{RP}^3$, the lens spaces $L(3,1)$ and $L(4,1)$ and the cube space $S^3/Q$. The creation of such a census is a highly non-trivial task, for details see \cite{LutzSul}.

Here is a table of the number of triangulations in the census at each topological type and diameter.\vspace{.1in}

\begin{tabular} {| l l | l l | l l | l l | l l |}
\hline
\multicolumn{2}{|c|}{$S^{3}/Q$} &
\multicolumn{2}{|c|}{$L(3,1)$} &
\multicolumn{2}{|c|}{$RP^{3}$} &
\multicolumn{2}{|c|}{$S^{3}$} &
\multicolumn{2}{|c|}{$L(4,1)$} \\
\hline
\hline
$1H$&1    &$2E$&1    &$1H$&10    &$1E$&3    &$1J$&1 \\
  &       &$1J$&1    &$2E$&7     &$1H$&173  &    &  \\
  &       &  &       &$1J$&5     &$2E$&401  &    &  \\
  &       &  &       &    &      &$1J$&2438 &    &  \\
  &       &  &       &    &      &$3E$&1060 &    &  \\
  &       &  &       &    &      &$2H$&582  &    &  \\
  &       &  &       &    &      &$4E$&93   &    &  \\
  &       &  &       &    &      &$2J$&11   &    &  \\
\hline
\end{tabular}\vspace{.1in}

\noindent Here is a table of the number of triangulations at each diameter. \vspace{.1in}

@@

\section{Algorithm Used}
